On verifying AhirV2 generated VHDL using software testbenches

### 2011-08-16 v2/CtestBench/docs/CtestBench.tex
Some documentation in order..

>>>>

\section{An example}

Consider the following program (lets say it is in file ``prog.c''):
\begin{verbatim}
#include <stdlib.h>
#include <stdint.h>
#include <stdio.h>
#include <iolib.h>

uint32_t sum;

void set_sum(uint32_t x)
{
    sum = x;
}

uint32_t get_sum()
{
    return(sum);
}

void accumulate()
{
    while(1)
    {
        int nxt = read_uint32("in_data");
#ifdef SW
        printf("read %u\n", nxt);
#endif
        sum = (sum + nxt);
        write_uint32("out_data",sum);
#ifdef SW
        printf("wrote %u\n", sum);
#endif
    }
}

\end{verbatim}

This program describes a {\em system} which listens
for data on a pipe ``in\_data'', and sends data
out on a pipe ``out\_data''.  The incoming data
is accumulated into the variable {\em sum}, and
there are two methods to set and get the value
of {\em sum}.

Now to test this program, we can write a test-bench
such as this one (lets call this file ``testbench.c'').
\begin{verbatim}
#include <pthread.h>
#include <signal.h>
#include <stdio.h>
#include <stdlib.h>

#ifdef SW 
// for the read_*/write_* methods
#include <iolib.h>
#include "prog.h"
#else
// includes for the read_*/write_* methods
// as well as stubs for functions moved
// to hardware.
#include "vhdlCStubs.h"
#endif

void Exit(int sig)
{
   fprintf(stderr, "## Break! ##\n");
   exit(0);
}

void *accumulate_(void* fargs)
{
   accumulate();
}

void *write_pipe_(void* a)
{
   write_uint32_n("in_data",(uint32_t*)a, 10);
}

void *read_pipe_(void* a)
{
   read_uint32_n("out_data",(uint32_t*)a, 10);
}

int main(int argc, char* argv[])
{
        signal(SIGINT,  Exit);
        signal(SIGTERM, Exit);

        uint32_t data_in[10], data_out[10];
        int i;

        // initial value of sum.
        set_sum(1);

        for(i = 0; i < 10; i++)
        {
          data_in[i] = i;
        }

        pthread_t acc_t, wpipe_t, rpipe_t;

#ifdef SW
        pthread_create(&acc_t,NULL,&accumulate_,NULL);
#endif
        pthread_create(&wpipe_t,NULL,&write_pipe_,(void*)data_in);
        pthread_create(&rpipe_t,NULL,&read_pipe_,(void*)data_out);

        pthread_join(wpipe_t,NULL);
        pthread_join(rpipe_t,NULL);

        fprintf(stdout,"from out_data, we read ");
        for(i=0; i < 10; i++)
          fprintf(stdout," %u ", data_out[i]);
        fprintf(stdout,"\n");
        fprintf(stdout,"final sum is %u\n", get_sum());

#ifdef SW
        pthread_cancel(acc_t);
#endif
}

\end{verbatim}
The test-bench sets an initial value for sum, and starts
three threads: one to write data to pipe in\_data, one
to read data from pipe out\_data, and one to run the
accumulate function.  After the last data is read back
from out\_data, the test-bench gets the value of sum
and prints it out.

Obviously, we would prefer to use the same test-bench
to verify that the VHDL system generated from ``prog.c'' 
functions correctly.  
The difference is that instead of using methods in iolib,
the test-bench now uses methods in SocketLib.  Further, the
VHDL is executed in a VHDL simulator; the simulator communicates
with the testbench using sockets.
The {\em ifdef's} in the test-bench and the system program
indicate the difference between the pure software version
of the system-test-bench combination and the hardware-software
version.

\section{An example}

Look at the subdirectory ``example'' which contains the files ``prog.c'' and
``testbench.c''.  A Makefile and README are also present.  Its all quite
self-explanatory.
